Reproducibility in plant pathology: where do we stand and a way forward

### 2021-06-23 analysis/paper/paper.Rmd
Fix "lack of lack of" on line 153
Remove "the the"

In the biological sciences it is not always possible to use identical test material or perhaps the the time or resources are not available for full reproducibility, _e.g._, field trials that span years and locations or complex glasshouse experiments.
Therefore, we will follow Peng's [-@Peng2009] definition that provides clear guidelines for a minimum standard of "reproducible research":

@@

It goes without saying that plant pathologists already provide information on protocols and chemicals allowing for reproducibility. 
However, very often biological specimens such as strains, cultures or cultivars are often not available. 
These cases constitute a lack of a lack of reproducibility but will not be covered here.

>>>>

In the biological sciences it is not always possible to use identical test material or perhaps the time or resources are not available for full reproducibility, _e.g._, field trials that span years and locations or complex glasshouse experiments.
Therefore, we will follow Peng's [-@Peng2009] definition that provides clear guidelines for a minimum standard of "reproducible research":

@@

It goes without saying that plant pathologists already provide information on protocols and chemicals allowing for reproducibility. 
However, very often biological specimens such as strains, cultures or cultivars are often not available. 
These cases do constitute a lack of reproducibility but will not be covered here.
